First Attempt at a Comparison Matrix

### 2014-08-15 test-compare-codes.Rmd
Use unique n-grams for the denominator
Since `intersect()` finds the unique n-grams that match, not all the
matches, it is necessary to use the unique n-grams in the denominator
too. This shows that the comparisons are more favorable than we thought.
And most important, in the diagonal of the comparison matrix, a code
compared to itself now has a value of 1.

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
  ratio_matches_to_destination <- length(matches) / length(dest_code)
  return(ratio_matches_to_destination)
}
```

@@

A big surprise is why the diagonal is not all `1`, since presumably a code is perfectly derived for itself. The reason is that the `intersect` function that we use to find matches must return only unique matches not duplicated matches. In other words, the intersection of a vector with itself is the same thing as the unique values of the vector. Proof:

```{r}
identical(intersect(codes_grams$NY1850.txt, codes_grams$NY1850.txt),
          unique(codes_grams$NY1850.txt))
```

That's a useful thing to know: maybe there is a better way to find matches. But for now let's not get sidetracked. The important point is that we can compare all of the codes into a matrix, and that it's pretty fast. Now we can run this analysis on the whole shebang.

First we get all the codes as n-grams:

>>>>

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(unique(shared_ngrams))
  ratio_matches_to_destination <- length(matches) / length(unique(dest_code))
  return(ratio_matches_to_destination)
}
```

@@

Now we can run this analysis on the whole shebang. First we get all the codes as n-grams:
